Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-10-01 Manuscript for submission/manuscript.tex
Update

%\begin{landscape}
\begin{table}[htbp]
\centering
\begin{tabular}{lclclcl}\hline
Pair & Community & Title & \\
\hline
1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         & \\
2    & MulT      & Innovated higher criticism for detecting sparse signals in correlated noise                   & \\
     & VarSel    & Regularized estimation of large covariance matrices & \\
3    & DimRed    & Contour projected dimension reduction & \\
     & VarSel    & Factor profiled sure independence screening & \\
4    & VarSel    & Factor profiled sure independence screening & \\
     & DimRed    & Sliced regression for dimension reduction & \\
5    & VarSel    & Covariance regularization by thresholding & \\
     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
6    & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       & \\
     & Mixed     & Marginal asymptotics for the ``large p small n'' paradigm: with applications to microarray data &  \\
7    & VarSel    & A majorization-minimization approach to Variable Selection using spike and slab priors        & \\
     & Mixed     & Empirical Bayes selection of wavelet thresholds & \\
8    & VarSel    & Spades and mixture models & \\
     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
9    & DimRed    & A constructive approach to the estimation of dimension reduction directions                   & \\
     & VarSel    & Factor profiled sure independence screening & \\
10   & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors        & \\
     & Mixed     & Spike and slab variable selection: Frequentist and Bayesian strategies                        & \\
11   & VarSel    & variable selection in nonparametric additive models & \\
     & Mixed     & Nonparametric estimation of an additive model with a link function                            & \\
12   & Mixed     & Nonparametric inferences for additive models & \\
     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models         & \\
13   & Mixed     & Bayesian variable selection in structured high-dimensional covariate spaces with applications in genomics & \\
     & VarSel    & Model selection and estimation in regression with grouped variables                           & \\
14   & VarSel    & The sparsity and bias of the LASSO selection in high-dimensional linear regression            & \\
     & Mixed     & Tests for high-dimensional covariance matrices & \\
15   & FuncAn    & Empirical dynamics for longitudinal data & \\
     & Mixed     & Variable selection in nonparametric varying-coefficient models for analysis of repeated measurements   &       \\\hline
\end{tabular}
\caption{All the $15$ edges come from pairs of papers from different communities. For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem.}
\end{table}
\label{tab:table2}
%\end{landscape}

@@

In proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}. Let $(M,M^{\perp})$ denote arbitrary subspace pair for which component-wise $L_{1}$ norm is decomposable. Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $M$ as $P_{M}$. And also note that proof relies on the following lemma:

\begin{lemma} \label{le:le1}
If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right)$, we have
\[
    \mathbb{Q}(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}) \leq
    \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\|_{F} +
    3\mathbb{Q}\left(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\right)+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
    \|S^{*}_{M^\perp}\|_{1}
\]
\end{lemma}

\noindent\textbf{proof of Theorem \ref{Th:th1}}.
\begin{proof}
Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal minimizer and feasible solution respectively for the convex program (\ref{eq:Modified}), we have
\begin{equation}\label{eq:2}
    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq
     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
\end{equation}

>>>>

%\begin{landscape}
\begin{table}[htbp]
\centering
\begin{tabular}{lclclcl}\hline
Pair & Community & Title & \\
\hline
1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                         & \\
2    & MulT      & Innovated higher criticism for detecting sparse signals in correlated noise                   & \\
     & VarSel    & Regularized estimation of large covariance matrices & \\
3    & DimRed    & Contour projected dimension reduction & \\
     & VarSel    & Factor profiled sure independence screening & \\
4    & VarSel    & Factor profiled sure independence screening & \\
     & DimRed    & Sliced regression for dimension reduction & \\
5    & VarSel    & Covariance regularization by thresholding & \\
     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
6    & VarSel    & Asymptotic properties of bridge estimators in sparse high-dimensional regression models       & \\
     & Mixed     & Marginal asymptotics for the ``large p small n'' paradigm: with applications to microarray data &  \\
7    & VarSel    & A majorization-minimization approach to Variable Selection using spike and slab priors        & \\
     & Mixed     & Empirical Bayes selection of wavelet thresholds & \\
8    & VarSel    & Spades and mixture models & \\
     & MulT      & Adapting to unknown sparsity by controlling the false discovery rate                          & \\
9    & DimRed    & A constructive approach to the estimation of dimension reduction directions                   & \\
     & VarSel    & Factor profiled sure independence screening & \\
10   & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors        & \\
     & Mixed     & Spike and slab variable selection: Frequentist and Bayesian strategies                        & \\
11   & VarSel    & variable selection in nonparametric additive models & \\
     & Mixed     & Nonparametric estimation of an additive model with a link function                            & \\
12   & Mixed     & Nonparametric inferences for additive models & \\
     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models         & \\
13   & Mixed     & Bayesian variable selection in structured high-dimensional covariate spaces with applications in genomics & \\
     & VarSel    & Model selection and estimation in regression with grouped variables                           & \\
14   & VarSel    & The sparsity and bias of the LASSO selection in high-dimensional linear regression            & \\
     & Mixed     & Tests for high-dimensional covariance matrices & \\
15   & FuncAn    & Empirical dynamics for longitudinal data & \\
     & Mixed     & Variable selection in nonparametric varying-coefficient models for analysis of repeated measurements   &       \\\hline
\end{tabular}
\caption{All the $15$ edges come from pairs of papers from different communities. For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem. But they are not related in terms of topic.}
\end{table}
\label{tab:table2}
%\end{landscape}

@@

In the proof, we use the notion of \emph{decomposable regularizer} which is studied at length in the work \cite{negahban2012unified}. Let $(M,M^{\perp})$ denote an arbitrary subspace pair for which component-wise $L_{1}$ norm is decomposable. Throughout the proof, we adopt the convenient short-hand notation on projection of matrix $P$ on subspace $M$ as $P_{M}$. And also note that the proof relies on the following lemma:

\begin{lemma} \label{le:le1}
If a pair of regularization parameters $(\delta,\gamma)$ satisfies condition (\ref{eq:49}), then for $\mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right)$, we have
\[
    \mathbb{Q}\left(\widehat{\Delta}^L_{B},\widehat{\Delta}^S_{M^\perp}\right) \leq
    \left\|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\right\|_{F} +
    3\mathbb{Q}\left(\widehat{\Delta}^{L}_{A},\widehat{\Delta}^{S}_{M}\right)+4 \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 4\frac{\gamma}{\delta}
    \left\|S^{*}_{M^\perp}\right\|_{1}
\]
\end{lemma}

\noindent\textbf{Proof of Theorem \ref{Th:th1}}.
\begin{proof}
Since $\widehat{\Theta}$ and $\Theta^{*}$ are optimal minimizer and feasible solution respectively for the convex program (\ref{eq:Modified}), we have
\begin{equation}\label{eq:2}
    h(\widehat{\Theta}) + \delta\|\widehat{L}\|_{*} + \gamma\|\widehat{S}\|_{1} \leq
     h(\Theta^{*}) + \delta\|{L^{*}}\|_{*} + \gamma\|{S}^{*}\|_{1}
\end{equation}
